SST_patterns

### 2019-10-15 SST_patterns.Rmd
Plot changes

```{r}
plot_loli_func <- function(df){
  ggplot(df, aes(x = date_peak, y = duration)) + 
  geom_lolli(aes(colour = intensity_cumulative)) + 
  scale_color_distiller(palette = "Spectral", name = "Cumulative \nintensity") + 
  facet_wrap(~distance, ncol = 2) +
  scale_y_continuous(breaks = c(5,10,15,20,25,30),
                     limits = c(1,30)) +
  xlab("Date (years)") + ylab("Event duration [days]") 
}

@@

combined_OISST_pl <- ggarrange(OISST_SP_pl, OISST_SB_pl, OISST_PN_pl,OISST_LB_pl)

@@

combined_CMC_pl <- ggarrange(CMC_SP_pl, CMC_SB_pl, CMC_PN_pl,CMC_LB_pl)

>>>>

```{r}
plot_loli_func <- function(df){
  ggplot(df, aes(x = date_peak, y = duration)) + 
  geom_lolli(aes(colour = intensity_cumulative)) + 
  scale_color_distiller(palette = "Spectral", name = "Cumulative \nintensity") + 
  facet_wrap(~distance, ncol = 2) +
  scale_y_continuous(breaks = c(5,10,15,20,25,30),
                     limits = c(1,30)) +
  theme_bw() +
  xlab("Date (years)") + ylab("Event duration [days]") 
}

@@

combined_OISST_pl_1 <- ggarrange(OISST_SP_pl, OISST_SB_pl)

combined_OISST_pl_2 <- ggarrange(OISST_PN_pl,OISST_LB_pl)

@@

combined_CMC_pl_1 <- ggarrange(CMC_SP_pl, CMC_SB_pl)

combined_CMC_pl_1 <- ggarrange(CMC_PN_pl,CMC_LB_pl)
